\textls[-0]{\thetitle}

### 2023-03-15 coqimpl.tex
edit on "trusted base" para

We implement our language design as a Coq plugin.
Rather than modifying the Coq kernel, a prototypical implementation as a
plugin allows a clearly defined trusted base and
improved compatibility with different versions of Coq.

The implementation works by translating programs in \Lang syntax into
programs that can be checked and evaluated by Coq.
The translation is compatible with interactive theorem proving (\ref{chg:tooling}), in that
a family is translated piece by piece, allowing each field to be defined
and checked separately.
The translation is modular and efficient\EDJ{I am very hesitant to say efficient :( }, in that
code compiled for fields of a base family
can be shared with derived families without having to be rechecked.

@@

\noindentparagraph{Trusted base.} Finally, we emphasize that our compilation can make sure the trusted code base is restricted to the Coq's kernel, as all the feature supported by our plugin has been compiled into Coq's surface syntax/Vernacular commands.

>>>>

We implement our language design as a Coq plugin.
%
It works by translating programs in \Lang syntax into
programs that can be checked and evaluated by Coq.
The translation is compatible with interactive theorem proving (\ref{chg:tooling}), in that
a family is translated piece by piece, allowing each field to be defined
and checked separately.
The translation is modular and efficient\EDJ{I am very hesitant to say efficient :( }, in that
code compiled for fields of a base family
can be shared with derived families without having to be rechecked.

@@

\noindentparagraph{Trusted base.}

Rather than modifying the Coq kernel to extend its core theory, a translation to
Coq conveniently reduces the trusted base of any development using \Lang to Coq.
%and improves compatibility with different versions of Coq.
In particular, once a family is closed, \lsti{Print Assumptions} can be used
to verify that there are no lingering \lsti{Axiom}s introduced by the translation.
Ramifications of possible bugs in the \Lang implementation are limited to
the usability of the plugin.
%Finally, we emphasize that our compilation can make sure the trusted code base is restricted to the Coq's kernel, as all the feature supported by our plugin has been compiled into Coq's surface syntax/Vernacular commands.
